\section{Introduction}

The exploration of new programmable architectures, and the development of innovative algorithms involved
in their commercial requires a robust CAD and architectural software synthesis flow that permits experimentation.
In order to model modern and future architectures, such a software flow is necessarily quite complex, and largely beyond the
capacity of any single academic enterprise to create, evolve and maintain.  Equivalent commercial flows are
supported by hundreds of full-time engineers.  Equally important to serve the same needs is a set of relevant
large-scale circuit benchmarks that can be used to test architectures and algorithms.
This paper describes the status of a global collaboration attempting to provide such a framework, describing
several innovations with the three main parts of the tool flow, new work to create robust benchmarks, and 
an illustration of the flow's ability to explore a new kind of hard logic block.

One of the goals of this project is to create a place where enhancements by others can be more easily integrated
into the suite of tools, rather than being orphaned, as is often the case.  This can be challenging as making
a flow robust requires more work than a typical academic project and publication requires.

This paper is organized as follows:  the next section gives an overview of the entire, flow describing its various inputs
and outputs.  The three subsequent sections describe the individual portions of the flow, and the new features just
becoming available.  In Section 6 we describe the work to develop larger, modern benchmarks, and describe the currently
available suite, and some data making it through the flow.  Section 7 provides a case study of the use of the flow to replicate previous work (done on an branch
of the VPR\cite{betz_vpr99}) to model floating-point logic blocks.  Section 8 outlines the extensive set of future work we see as necessary
to continue this work.
